Cofinality and the Delta System Lemma

### 2020-11-27 Delta_System_Lemma/document/root.tex
renombrando "Edwin"
document preparation for Cofinality and Delta System Lemma

@@

\title{Formalization of Forcing in Isabelle/ZF}
\author{Emmanuel Gunther
  \and 
  Miguel Pagano
  \and 
  Pedro S\'anchez Terraf
}
\maketitle

>>>>

\input{header-delta-system}

@@

\title{Cofinality and the Delta System Lemma}
\author{
  Pedro S\'anchez Terraf\thanks{Universidad Nacional de C\'ordoba. 
    Facultad de Matem\'atica, Astronom\'{\i}a,  F\'{\i}sica y
    Computaci\'on.}
  \thanks{%
    Centro de Investigaci\'on y Estudios de Matem\'atica
    (CIEM-FaMAF), Conicet. C\'ordoba. Argentina.
    Supported by Secyt-UNC project 33620180100465CB.}
}
\maketitle

\begin{abstract}
  We formalize the basic results on cofinality of linearly ordered
  sets and ordinals and \v{S}anin's Lemma for uncountable families of
  finite sets. We work in the set theory framework of
  Isabelle/ZF, using the Axiom of Choice as needed.
\end{abstract}
